ששש

## 1. A preliminary look at the Bustabit data


```{r}
# Load the tidyverse
library(tidyverse)

# Read in the bustabit gambling data 
bustabit <- read_csv("C:/Users/yoavr/Google Drive/Datacamp/PROJECT CLUSTERING BUSTABIT GAMBLING BEHAVIOR/bustabit.csv")

# Look at the first five rows of the data
head(bustabit)
# Find the highest multiplier (BustedAt value) achieved in a game
bustabit %>%
    arrange(desc(BustedAt)) %>%
    slice(1)
```


## 2. Deriving relevant features for clustering


```{r}
# Create the new feature variables 
bustabit_features <- bustabit %>% 
  mutate(CashedOut = ifelse(is.na(CashedOut), BustedAt + .01, CashedOut),
         Profit = ifelse(is.na(Profit), 0, Profit),
         Losses = ifelse(Profit == 0, -1 * Bet, 0),
         GameWon = ifelse(Profit == 0, 0, 1),
         GameLost = ifelse(Losses < 0, 1, 0))

head(bustabit_features)

```

## 3. Creating per-player statistics


```{r}
# Group by players to create per-player summary statistics
bustabit_clus <- bustabit_features %>%
  group_by(Username) %>%
  summarize(AverageCashedOut = mean(CashedOut), 
            AverageBet = mean(Bet),
            TotalProfit = sum(Profit),
            TotalLosses = sum(Losses), 
            GamesWon = sum(GameWon),
            GamesLost = sum(GameLost))

# View the first five rows of the data
head(bustabit_clus, n = 5)
```



## 4. Scaling and normalization of the derived features


```{r}
# Create the mean-sd standardization function
mean_sd_standard <- function(x) {
    (x - mean(x)) / sd(x)
}

# Apply the function to each numeric variable in the clustering set
bustabit_standardized <- bustabit_clus %>%
    mutate_if(is.numeric, mean_sd_standard)
              
# Summarize our standardized data
summary(bustabit_standardized)
```



## 5. Cluster the player data using K means
<p>With standardized data of per-player features, we are now ready to use K means clustering in order to cluster the players based on their online gambling behavior. K means is implemented in R in the <code>kmeans()</code> function from the stats package. This function requires the <code>centers</code> parameter, which represents the number of clusters to use. </p>
<p>Without prior knowledge, it is often difficult to know what an appropriate choice for the number of clusters is. We will begin by choosing <strong>five</strong>. This choice is rather arbitrary, but represents a good initial compromise between choosing too many clusters (which reduces the interpretability of the final results), and choosing too few clusters (which may not capture the distinctive behaviors effectively). Feel free to play around with other choices for the number of clusters and see what you get instead!</p>
<p>One subtlety to note - because the K means algorithm uses a random start, we are going to set a random seed first in order to ensure the results are reproducible.</p>


```{r}
# Choose 20190101 as our random seed
set.seed(20190101)

# Cluster the players using kmeans with five clusters
cluster_solution <- kmeans(bustabit_standardized %>% select(-Username), 5)

# Store the cluster assignments back into the clustering data frame object
bustabit_clus$cluster <- factor(cluster_solution$cluster)

# Look at the distribution of cluster assignments
table(bustabit_clus$cluster)
```



## 6. Compute averages for each cluster
<p>We have a clustering assignment which maps every Bustabit gambler to one of five different groups. To begin to assess the quality and distinctiveness of these groups, we are going to look at <strong>group averages</strong> for each cluster across the original variables in our clustering dataset. This will, for example, allow us to see which cluster tends to make the largest bets, which cluster tends to win the most games, and which cluster tends to lose the most money. This will provide us with our first clear indication as to whether the behaviors of the groups appear distinctive!</p>


```{r}
# Group by the cluster assignment and calculate averages
bustabit_clus_avg <- bustabit_clus %>%
    group_by(cluster) %>%
    summarize_if(is_numeric, mean)

# View the resulting table
bustabit_clus_avg
```


## 7. Visualize the clusters with a Parallel Coordinate Plot
<p>We can already learn a bit about our cluster groupings by looking at the previous table. We can clearly see that there is a group that makes very large bets, a group that tends to cash out at very high multiplier values, and a group that has played many games of Bustabit. We can visualize these group differences graphically using a Parallel Coordinate Plot or PCP. To do so, we will introduce one more kind of scaling: min-max scaling, which forces each variable to fall between 0 and 1.</p>
<p>Other choices of scaling, such as the Z-score method from before, can work effectively as well. However, min-max scaling has the advantage of <strong>interpretability</strong> - a value of 1 for a particular variable indicates that cluster has the highest value compared to all other clusters, and a value of 0 indicates that it has the lowest. This can help make relative comparisons between the clusters more clear.</p>
<p>The <code>ggparcoord()</code> function from <code>GGally</code> will be used to produce a Parallel Coordinate Plot. Note that this has a built-in argument <code>scale</code> to perform different scaling options, including min-max scaling. We will set this option to <code>"globalminmax"</code> to perform no scaling, and write our own scaling routine for practice. If you are interested, you can look at the function definition for <code>ggparcoord()</code> to help you write our scaling function!</p>


```{r}
# Create the min-max scaling function
min_max_standard <- function(x) {
    (x - min(x)) / (max(x) - min(x)) 
}

# Apply this function to each numeric variable in the bustabit_clus_avg object
bustabit_avg_minmax <- bustabit_clus_avg %>%
    mutate_if(is.numeric, min_max_standard)

# Load the GGally package
library(GGally)
              
# Create a parallel coordinate plot of the values
ggparcoord(bustabit_avg_minmax, columns = 2:7, 
           groupColumn = 1, scale = "globalminmax", order = "skewness")
```


## 8. Visualize the clusters with Principal Components
<p>One issue with plots like the previous is that they get more unwieldy as we continue to add variables. One way to solve this is to use the Principal Components of a dataset in order to reduce the dimensionality to aid in visualization. Essentially, this is a two-stage process:</p>
<ol>
<li>We extract the principal components in order to reduce the dimensionality of the dataset so that we can produce a scatterplot in two dimensions that captures the underlying structure of the higher-dimensional data.</li>
<li>We then produce a scatterplot of each observation (in this case, each player) across the two Principal Components and color according to their cluster assignment in order to visualize the separation of the clusters.</li>
</ol>
<p>This plot provides interesting information in terms of the similarity of any two players. In fact, you will see that players who fall close to the boundaries of clusters might be the ones that exhibit the gambling behavior of a couple of different clusters. After you produce your plot, try to determine which clusters seem to be the most "different." Also, try playing around with different projections of the data, such as PC3 vs. PC2, or PC3 vs. PC1, to see if you can find one that better differentiates the groups.</p>


```{r}
# Calculate the principal components of the standardized data
my_pc <- as.data.frame(prcomp(bustabit_standardized %>% select_if(is_numeric))$x)

# Store the cluster assignments in the new data frame
my_pc$cluster <- bustabit_clus$cluster

# Use ggplot() to plot PC2 vs PC1, and color by the cluster assignment
p1 <- ggplot(my_pc, aes(x = PC1, y =  PC2, col = cluster)) +
             geom_point()

# View the resulting plot
p1
```


## 9. Analyzing the groups of gamblers our solution uncovered
<p>Though most of the statistical and programmatical work has been completed, possibly the most important part of a cluster analysis is to interpret the resulting clusters. This often is the most desired aspect of the analysis by clients, who are hoping to use the results of your analysis to inform better business decision making and actionable items. As a final step, we'll use the parallel coordinate plot and cluster means table to interpret the Bustabit gambling user groups! Roughly speaking, we can breakdown the groups as follows:</p>
<p><strong><p style="color:#d95f02">Cautious Commoners:</p></strong> This is the largest of the five clusters, and might be described as the more casual Bustabit players. They've played the fewest number of games overall, and tend to make more conservative bets in general. </p>
<p><strong><p style="color:#66a61e">Strategic Addicts:</p></strong> These users play a lot of games on Bustabit, but tend to keep their bets under control. As a result, they've made on average a net positive earnings from the site, in spite of having the most games played. They seem to maintain a strategy (or an automated script/bot) that works to earn them money.</p>
<p><strong><p style="color:#7570b3">Risky Commoners:</p></strong> These users seem to be a step above the Cautious Commoners in their Bustabit gambling habits, making larger average bets, and playing a larger number of games on the site. As a result, though they have about the same number of average games won as the Risk Takers, they have a significantly higher number of games lost.</p>
<p><strong><p style="color:#1b9e77">Risk Takers: </p></strong> These users have played only a couple games on average, but their average cashed out value is significantly higher than the other clusters, indicating that they tend to wait for the multiplier to increase to large values before cashing out.</p>
<p><strong><p style="color:#e7298a">High Rollers:</p></strong> High bets are the name of the game for this group. They bet large sums of money in each game, although they tend to cash out at lower multipliers and thus play the game more conservatively, particularly compared to the Risk Takers. Interestingly, these users have also on average earned a net positive earnings from their games played.</p>


```{r}
# Assign cluster names to clusters 1 through 5 in order
cluster_names <- c(
    "Risky Commoners",
    "High Rollers",
    "Risk Takers",
    "Cautious Commoners",
    "Strategic Addicts"
)

# Append the cluster names to the cluster means table
bustabit_clus_avg_named <- bustabit_clus_avg %>%
    cbind(Name = cluster_names)

# View the cluster means table with your appended cluster names
bustabit_clus_avg_named
```


